Let’s Disco – Publishing person-level data as Linked Data.

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial
ESWC 2015 Tutorial abstract

%
%
\title{Let’s Disco – Publishing person-level data as Linked Data.}
\subtitle{Building a Data Portal with DCAT, DDI-RDF Discovery, PHDD, and other vocabularies.\bz{Ben's Kommentar}
}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXX\inst{1} \and XXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
\and
Albstadt-Sigmaringen University, Germany \\
\email{nolle@hs-albsig.de}
}

@@

\begin{abstract}
200 words

\keywords{RDF Validation, RDF Constraints, OWL 2 QL, OWL 2 DL, Reasoning, RDF Validation Requirements, Linked Data, Semantic Web}
\end{abstract}
%

@@

The DDI-RDF Discovery Vocabulary (Disco) is a RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.

@@

>>>>

%
%
\title{Let’s Disco – Publishing person-level data as Linked Data.}
\subtitle{Building a Data Portal with DCAT, DDI-RDF Discovery, PHDD, and other vocabularies.\bz{Ben's Kommentar}
}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXX\inst{1} \and XXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{\{benjamin,thomas\}}.bosch@gesis.org}

@@

\begin{abstract}
The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
 The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.

For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, and Physical Data Description) are reused to a large extend. 
The workshop organizers show how Disco is interwoven with these vocabularies. 
The combined usage of Physical Data Description, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.

In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems.

\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata, Microdata Metadata, Discovery of Microdata, Data Documentation Initiative, DDI, Linked Data, Semantic Web}
\end{abstract}
%

@@

The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.

@@

\tb{we could provide full day if we make the hands on exercises with the SPARQL queries / do you think we should do that?}
